### 2016-08-25 ms/ms.tex
worked on discussion

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de Sao Paulo\\
    Sao Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity their component guilds of species, these
systems are particularly at risk from coextinction cascades. The
nature of these coextinction cascades depends on the interaction
patterns within a community \citep{Memmott2004, Rezende2007,
  Bascompte2009}. Recovering the lost biodiversity and interactions
through ecological restoration has become increasingly imperative, and
a key restoration aim is to facilitate assembly of robust interaction
networks \citep{menz-2010-4}. We know little, however, about how to
re-assemble interacting communities through restoration, or the
process of ecological network assembly more generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The mostly widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that a new species
is more likely to interact with species that are already
well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, likely because these species are either more abundant or more
temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some indication
assembly was occurring through preferential attachment. Network
nestedness, a pattern of interactions where a generalist core
interacts with both specialist and generalist species, increased as
the community aged \citep{albrecht2010plant}. Increasing nestedness
could result from a process like preferential attachment where
specialist species attach to the well-connected, generalist core.  In
addition, non-successional temporal dynamics also suggest a stable
core of generalists persists despite high turnover of peripheral
species \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, assembly can be punctuated by significant reorganizations
of interactions \citep{peel2014detecting}. Such significant
reorganizations of interactions, or changing points, have been
observed in social networks responding to abrupt shifts in the
behavior of interactors \citep{peel2014detecting}.  In ecological
communities, such shifts my occur if, as new species are added,
resident species change their interaction partners to optimize their
foraging effort. In plant-pollinator communities, theory predicts
pollinators optimize their use of floral resources to reduce
interspecific competition and improve resource-use efficiency
\citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined whether changing points occur during
ecological network assembly and how they relate to the behavior of the
interactors.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,]{parker1997scale}. In pollination systems, the time since
an area was restored has been shown to effect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as the
community develops. Understanding the mechanisms of network assembly
will help to guide the restoration of particular communities.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating effective restoration of networks is especially
imperative in areas where species interactions provide essential
ecosystem services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which have the capacity to provide
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure provision the continued provision
of ecosystem services and curb biodiversity loss, effective
restoration of pollinators and their interactions in agricultural
landscapes is critical.

%% hedgerows!!  
To promote pollinator services in agriculture, farmers are
increasingly turning to the habitat restoration technique of planting
strips of native plants along farm edges (hedgerows) to help provide
habitat for pollinators without removing arable land from
production. Hedgerows have been shown to augment the richness,
abundance and trait diversity of pollinators in agricultural
landscapes\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known however, about the assembly
of the network following hedgerow restoration.

Using a long-term data-set of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., changing points). Even with changing points in
interaction organization, networks could still be assembling via
preferential attachment if the network reorganizations were primarily
driven the by peripheral, temporally variable species while a stable,
well-connected core of species still persists. We thus examine whether
the species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species.  Lastly, we examine whether networks are
assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is comprised of
intensively managed agriculture -- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production, and are ca. 3--6m wide and approximately 350m long and
border large (ca.\ 30--hectare) crop fields. Hedgerows consist of
native, perennial, shrub and tree plantings including \textit{Rosa
  californica}, \textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep{kremen-2015-602, mgonigle-2015-x}. The mean
distance between monitoring sites was 15 km, and the minimum distance
between sites of the same type sampled in the same year was 2 km.  The
entire area surveyed spanned almost 300 km$^2$. The crop fields
adjacent to all sites were similarly managed as intensive, high-input
monoculture.

Monitoring began in 2006 and continued through 2015. Sampling of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of
sampling, the order in which sites were sampled was
randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A.~Klein and L.~Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

Quantitative networks were generative for each site through time. To
account for the unequal number of surveys between years, the mean of
the interactions between a pair of plants and pollinators across
surveys within a year was used as a representation of the frequency of
interactions.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental changes in large-scale pattern of interactions
of plants and pollinators. A change point is caused by a merge, split,
fragmentation or formation of communities (also called modules or
compartments). Change point detection methods have yet to be
generalized to quantitative networks, so for this analysis we focused
on qualitative (binary) networks. Following \cite{peel2014detecting},
we first defined a probability distribution over the networks using
the generalized hierarchical random graph model (GHRG). The GHRG model
is able to capture both assortative and disassortative community
structure patterns at all scales in the network
\citep{peel2014detecting}. A network $G$ is composed of vertices $V$
and edges $E \subseteq {V × V }$. The GHRG model decomposes the $N$
vertices into a series of nested groups, the relationships among which
are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ thus defined as:

@@

Using Bayesian posterior inference and techniques from phylogenetic
tree reconstruction, we fit the GHRG model to the networks
\citep{peel2014detecting}. This is accomplished by using a Markov
Chain Monte Carlo (MCMC) procedure to first sample the posterior
distribution of bipartitions, from which a consensus tree is derived
\citep{peel2014detecting}. We used $\beta$ distributions with the
hyperparameters $\alpha=\beta=1$ to define priors for $p_r$.

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models -- one where a change point
had occurred between two networks, and one where no change occurred --
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of nine years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. The change
point analysis was carried out using code published online by
L.~Peel. Analyses we conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. For the
non-assembling hedgerows and weedy field margins, only sites with five
or greater years of sampling was included in this analysis. All
statistical analysis were conducted in R 3.2.3 \citep{R}.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed the reorganization of
interactions. Some species remain in relatively similar network
positions through time, whereas others are more variable in their role
and thus contribute more strongly to network reorganization. We test
the that more persistent species with the highest degree are the most
stable in their network position, as would be expected is the networks
were assembling via preferential attachment.

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. %% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and the distribution of the interaction
frequencies \citep{Galeano2009}. Lastly, Network specialization was
measured using H2, which estimate the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from 0 for generalized
networks to 1 for specialized networks.

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we simulate
the extinction of plant species the subsequent extinction cascades of
pollinator species. Because the reproduction of plant species if
facilitated by active restoration efforts, it is unlikely the
extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is used as a
measure of network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed as
community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to how difficult it is to turn a network
into completely disconnected groups of nodes, or species
\citep{costa2007characterization} --- the larger the algebraic
connectivity, the more robust a network is to cascading perturbations
(Gaiarsa et al., submitted), and the harder it is to break the
community into isolated groups of species.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{The network structure and changing points (vertical red
    lines) in assembling hedgerows and a representative sample of
    non-assembling hedgerows and weedy field margins. In each network,
    plants and pollinators are represented by green and yellow
    circles, respectively, weighted by their degree. Each species has
    has a consistent position in the network across years. In the
    assembling hedgerows, colored squares in the corner of each
    network represent the years post restoration.}
  \label{fig:changePoints}
\end{figure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{The change in nestedness, modularity, specialization and
    connectance as the networks assemble. The left panels represent
    $z$-scores. Scores greater than $\sim 2$ or less than $\sim -2$
    are significantly more or less structured than randomly assembled
    networks. Points are the value for each site at each year of
    assembly. The solid line indicates the mean slope estimate and the
    dashed lines are the $95\%$ confidence intervals around the
    estimate.}
  \label{fig:baci}
\end{figure}
\clearpage

>>>>

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de Sao Paulo\\
    S{\~a}o Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity their component guilds of species, these
systems are particularly at risk from coextinction cascades. The
nature of these cascades will depend on the interaction patterns
within a community \citep{Memmott2004, Rezende2007,
  Bascompte2009}. Recovering the lost biodiversity and interactions
through ecological restoration has become increasingly imperative, and
a key restoration aim is to facilitate assembly of robust interaction
networks \citep{menz-2010-4}. We know little, however, about how to
re-assemble interacting communities through restoration, or the
process of ecological network assembly more generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The most widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that a new species
is more likely to interact with species that are already
well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some indication
assembly occurred through preferential attachment. Network nestedness,
a pattern of interactions where a generalist core interacts with both
specialist and generalist species, increased as the community aged
\citep{albrecht2010plant}. Increasing nestedness could result from
preferential attachment process where specialist species attach to the
well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or changing points, are observed in social networks
responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}.  In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the behavior of the interactors.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,]{parker1997scale}. In pollination systems, the time since
an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating effective restoration of networks is especially
imperative in areas where species interactions provide essential
ecosystem services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which are capable of providing
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure provision the continued provision
of ecosystem services and curb biodiversity loss, effective
restoration of pollinators and their interactions in agricultural
landscapes is critical.

%% hedgerows!!  
To promote pollinator services in agriculture, farmers are
increasingly turning to the habitat restoration technique of planting
strips of native plants along farm edges (hedgerows) to help provide
habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural
landscapes\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about the assembly
of the network following hedgerow restoration.

Using a long-term dataset of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species still persists. We test
whether the species are most variable in their network position ---
and thus important contributors network reorganizations --- are less
persistent and connected species. To further explore the mechanisms
underlying the temporal dynamics in the networks, we examine patterns
in the species and interaction temporal turnover. Lastly, we
investigate whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is comprosed of
intensively managed agriculture -- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca. 3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

Monitoring began in 2006 and continued through 2015. Surveys of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of sampling, the order in which sites
were sampled was randomized. Surveys were conducted under sunny
conditions when the temperature was above $21^{\circ}\mathrm{C}$ and
wind speed was below $2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by hive
placement by bee-keepers. All other insect flower visitors that
touched the reproductive parts of the flower were collected; however,
here we focus only on wild bees and syrphids --- the most abundant and
effective pollinators in the system (representing 49 and 19 percent of
records, respectively, C.~Kremen, A.~Klein and L.~Morandin,
unpublished data). Bee and syrphid specimens were identified to
species (or morpho-species for some bee specimens in the genera
\textit{Nomada} and \textit{Sphecodes}) by expert taxonomists.

Quantitative networks were generated for each site through time. To
account for the unequal number of surveys between years (Tables
S1-S3), we use the mean of the interactions between a pair of plants
and pollinators across surveys within a year to represent intearction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of communities (also called modules or compartments). Change
point detection methods have yet to be generalized to quantitative
networks, so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E \subseteq {V × V
}$. The GHRG model decomposes the $N$ vertices into a series of nested
groups, the relationships among which are represented by the
dendrogram $T$. The tips of $T$ are the vertices of $G$, and the
probability that two vertices $u$ and $v$ connect is given by the
parameter $p_r$. The probability distribution of the network $G$ thus
defined as:

@@

Using Bayesian posterior inference and techniques from phylogenetic
tree reconstruction, we fit the GHRG model to the networks
\citep{peel2014detecting}. This is accomplished by using a Markov
chain Monte Carlo (MCMC) procedure to first sample the posterior
distribution of bipartitions, from which a consensus tree is derived
\citep{peel2014detecting}. We use $\beta$ distributions with the
hyperparameters $\alpha=\beta=1$ to define priors for $p_r$.

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of nine years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We emploied
code published online by L.~Peel for the change point
analysis. Analyses we conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis. All statistical analysis
were conducted in R 3.2.3 \citep{R}.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their role
and thus contribute more strongly to network reorganization. We test
the that more persistent species with the highest degree are the most
stable in their network position, as would be expected is the networks
were assembling via preferential attachment.

We calculate species persistence as the proportion of surveys a plant
or pollinator is observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations from an extensive dataset
from Yolo County (approx.~18000 interaction records) that included
both the data included in this study and additional data from sites
where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness at each site through time. Closeness describes the
centrality of a species in the network by calculating path lengths to
other vertices (species) in the graph. We use linear mixed models to
test whether the species closeness variability (log) is related to the
persistence or degree of that species \citep{lme4, lmetest}. We
included random effects for species, as well as site. Because the
degree and persistence of pollinators were strongly correlated, ($\rho
= 0.84$, $p$-value $<$ $2*10^{-16}$), we include each explanatory
variable in the model separately. Plant degree and persistent were not
significantly correlated, but we use the same models as we did for the
pollinators for consistency. A linear increase in closeness, as might
be expected with assembly by preferential attachment, would also lead
to a high variability in closeness scores, so we test whether
closeness increases through time.

\subsection*{Species and interaction turnover}

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. Assembling networks may have higher
rates of species turnover than non-assembling communities because new
species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities.

To estimate the temporal turnover of species and interactions, we use
an approach similar to calculating spatial $\beta$-diversity. Instead
of calculating the variation in community composition across sites
within a year, however, we estimated turnover across years at a
site. We first calculated the pairwise dissimilarity of species and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were response variables in
a linear mixed models with site type as an explanatory variable along
with random effects for both year and site \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develope a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

\section*{Temporal changes in interaction patterns}

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. The connectance
of a network (the proportion of observed out of possible interaction),
is realted to the

The specialization 
The colonization of specialist species or species are beginning to
limit their interaction niche breath as the network assembles would
lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we use
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. Lastly, Network specialization was measured using
H2, which estimate the deviation of the observed interaction frequency
between plants and pollinators from a null expectation where all
partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from 0 for generalized networks to
1 for specialized networks.

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we
simulate the extinction of plant species the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is an estimate of
network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to how
difficult it is to turn a network into completely disconnected groups
of vertexs, or species \citep{costa2007characterization} --- the larger
the algebraic connectivity, the more robust a network is to cascading
perturbations (Gaiarsa et al., submitted), and the harder it is to
break the community into isolated groups of species.

@@

@@
